\section{Introduction}

Analytical pipelines produce discrete outcomes that depend on how their inputs are represented. The same data, processed through the same computational engine under the same query, can yield different outcomes when the internal representation changes. Some representational changes leave the outcome intact; others alter it entirely.

In current practice, a pipeline runs under one representation, a result is reported, the sensitivity of that result to representational alternatives remains invisible. No recorded evidence distinguishes decisions that can be reused under representational change from those requiring renewed justification.

A \emph{decision-valued map} records which representations preserve the outcome and which change it, associating each member of a representation family with the discrete result the engine produces. Figure~\ref{fig:pipeline} summarizes the evaluation protocol used to construct such a map by varying representations within a single arena.

Every stage of the evaluation chain is logged as a content-addressed artifact stored in write-once form by DecisionDB, the system described in this paper. DecisionDB supports representational sweeps through systematic variation of declared representation parameters, replay verification through deterministic recovery of decision identifiers from persisted artifacts and post-hoc audit of the full provenance chain.

In a graph routing demonstration, two representation parameters that control edge-cost construction are swept while the graph snapshot and shortest-path engine remain constant. One parameter preserves decision identity across its tested range; the other induces a discrete identity change at a specific threshold. Replay verification recovers all persisted identifiers exactly.
